---
title: "SDS 237 - Field Journal"
author: "Janeth Covarrubias Perez"
date: "Last updated on `r Sys.Date()`"
output: pdf_document
---

> Instructions: For each journal entry, first fill out the metadata for that entry by entering your name, the date you observed a data environment, the date you wrote up your entry, and the location of the environment you observed in between the quotation marks of the associated code snippet. Be sure to enter the date as month/day/year. Below this code snippet, write your journal entry. Once your done, knit the document and push your changes to GitHub.

```{r libraries, include = FALSE}
library(lubridate)
```

## Journal Entry 1

```{r metadata_1, echo=FALSE, results='asis'}
observer_1 <- "FILL YOUR NAME"
date_observed_1 <- mdy("01/01/1990")
date_written_up_1 <- mdy("01/01/1990")
location_1 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_1, " observed on ", date_observed_1, " in ", location_1, ". The observations were written up on ", date_written_up_1, "."))
```

[Enter your write-up here.]

### Completion Checklist
> Enter an `x` between each [] in order to indicate that you're write-up meets the criteria.

[ ] Write-up is 300-400 words.
[ ] Write-up is *primarily about* a statistic, dataset, data standard, or data collection environment encountered in the past two weeks.
[ ] Write-up addresses the question: *What socio-cultural forces are at play in shaping this statistic, dataset, data standard, or data collection environment?*
[ ] Write-up references and defines a concept from the course's [*Knowledge and Understanding*](https://sds-237-data-ethnography.github.io/public-website-fall-23/learning_dimensions.html#knowledge-and-understanding) learning dimension.
[ ] **The referenced concept is specifically used to analyze the socio-cultural forces animating the data's cultural meaning.** 
[ ] The concept is **bolded** in the write-up. 

## Journal Entry 2 

```{r metadata_2, echo=FALSE, results='asis'}
observer_2 <- "FILL YOUR NAME"
date_observed_2 <- mdy("01/01/1990")
date_written_up_2 <- mdy("01/01/1990")
location_2 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_2, " observed on ", date_observed_2, " in ", location_2, ". The observations were written up on ", date_written_up_2, "."))
```

[Enter your write-up here.]

### Completion Checklist
> Enter an `x` between each [] in order to indicate that you're write-up meets the criteria.

[ ] Write-up is 300-400 words.
[ ] Write-up is *primarily about* a statistic, dataset, data standard, or data collection environment encountered in the past two weeks.
[ ] Write-up addresses the question: *What socio-cultural forces are at play in shaping this statistic, dataset, data standard, or data collection environment?*
[ ] Write-up references and defines a concept from the course's [*Knowledge and Understanding*](https://sds-237-data-ethnography.github.io/public-website-fall-23/learning_dimensions.html#knowledge-and-understanding) learning dimension.
[ ] **The referenced concept is specifically used to analyze the socio-cultural forces animating the data's cultural meaning.** 
[ ] The concept is **bolded** in the write-up. 

## Journal Entry 3

```{r metadata_3, echo=FALSE, results='asis'}
observer_3 <- "FILL YOUR NAME"
date_observed_3 <- mdy("01/01/1990")
date_written_up_3 <- mdy("01/01/1990")
location_3 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_3, " observed on ", date_observed_3, " in ", location_3, ". The observations were written up on ", date_written_up_3, "."))
```

[Enter your write-up here.]

### Completion Checklist
> Enter an `x` between each [] in order to indicate that you're write-up meets the criteria.

[ ] Write-up is 300-400 words.
[ ] Write-up is *primarily about* a statistic, dataset, data standard, or data collection environment encountered in the past two weeks.
[ ] Write-up addresses the question: *What socio-cultural forces are at play in shaping this statistic, dataset, data standard, or data collection environment?*
[ ] Write-up references and defines a concept from the course's [*Knowledge and Understanding*](https://sds-237-data-ethnography.github.io/public-website-fall-23/learning_dimensions.html#knowledge-and-understanding) learning dimension.
[ ] **The referenced concept is specifically used to analyze the socio-cultural forces animating the data's cultural meaning.** 
[ ] The concept is **bolded** in the write-up. 

## Journal Entry 4

```{r metadata_4, echo=FALSE, results='asis'}
observer_4 <- "Janeth Covarrubias"
date_observed_4 <- mdy("11/06/2023")
date_written_up_4 <- mdy("11/09/2023")
location_4 <- "Website"

cat(paste0("This entry documents a data environment ", observer_4, " observed on ", date_observed_4, " in ", location_4, ". The observations were written up on ", date_written_up_4, "."))
```

[For this fieldnote I looked at the latest **Episodic Television Director Inclusion** Report released by the Directors Guild of America (DGA), to understand the nuanced dynamics of diversity and inclusion in the television and film industry during the pandemic in 2020-21.
The report serves as an epistemological tool, providing a structured knowledge framework to comprehend the evolving landscape of diversity in the media industry. It shapes the discourse surrounding representation, offering insights into how knowledge about diversity is constructed, disseminated, and interpreted within the industry. This acts as a bridge between statistics and meaningful change, illustrating how data is transformed into strategies, policies, and initiatives for diversity and inclusion.
This report unveils the rituals involved in the creation of on-screen content. It exposes how the labor dynamics intersect with traditional industry practices and rituals, shaping the opportunities available to directors of color, especially women of color. I found a trend of persistent disparities, particularly for Latino, Asian, and Native American directors with 9%, 7% 1% respectively. 
The concept of power manifests in decisions made by studios, networks, and production companies, influencing who gets hired, what stories get told, and what seems worthy of showing on screen vs who gets to produce these stories. This report is interesting to me because the data was measured by counting the number of episodes directed by directors of color which makes me question who is considered “important” enough to collect data on. Within the film industry, there are a lot of people involved in completing a project but for this study, only the directors were asked to participate.
This is important because this report isn’t just data but becomes a tool to shape the industry's understanding of diversity and inclusion. The translation of data into actionable strategies is an infrastructure of change within the industry that has been dominated by white men since its beginnings. The labor rituals exposed by the report shed light on the day-to-day experiences of underrepresented directors and other film staff involved in the making of media, revealing both the challenges and opportunities that come with occupying these spaces. The incentives for diversity mobilize communities and film industries, showcasing the power of intentional efforts these two stakeholders can have to change narratives.
]

### Completion Checklist
> Enter an `x` between each [] in order to indicate that you're write-up meets the criteria.

[x] Write-up is 300-400 words.
[x] Write-up is *primarily about* a statistic, dataset, data standard, or data collection environment encountered in the past two weeks.
[x] Write-up addresses the question: *What socio-cultural forces are at play in shaping this statistic, dataset, data standard, or data collection environment?*
[x] Write-up references and defines a concept from the course's [*Knowledge and Understanding*](https://sds-237-data-ethnography.github.io/public-website-fall-23/learning_dimensions.html#knowledge-and-understanding) learning dimension.
[x] **The referenced concept is specifically used to analyze the socio-cultural forces animating the data's cultural meaning.** 
[x] The concept is **bolded** in the write-up. 

## Journal Entry 5

```{r metadata_5, echo=FALSE, results='asis'}
observer_5 <- "FILL YOUR NAME"
date_observed_5 <- mdy("01/01/1990")
date_written_up_5 <- mdy("01/01/1990")
location_5 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_5, " observed on ", date_observed_5, " in ", location_5, ". The observations were written up on ", date_written_up_5, "."))
```

[Enter your write-up here.]

### Completion Checklist
> Enter an `x` between each [] in order to indicate that you're write-up meets the criteria.

[ ] Write-up is 300-400 words.
[ ] Write-up is *primarily about* a statistic, dataset, data standard, or data collection environment encountered in the past two weeks.
[ ] Write-up addresses the question: *What socio-cultural forces are at play in shaping this statistic, dataset, data standard, or data collection environment?*
[ ] Write-up references and defines a concept from the course's [*Knowledge and Understanding*](https://sds-237-data-ethnography.github.io/public-website-fall-23/learning_dimensions.html#knowledge-and-understanding) learning dimension.
[ ] **The referenced concept is specifically used to analyze the socio-cultural forces animating the data's cultural meaning.** 
[ ] The concept is **bolded** in the write-up. 

